Adaptive broadcast tree for multicores

### 2013-06-04 graphs/visu_gruyere_binarytree.tex
Added forgotten file

\node at (0mm,480mm) {Machine: gruyere, topology: badtree};
\node[draw,fill=red!20,minimum size=10mm] (s_0_14) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_28) at (60mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_14) at (90mm,210mm) {};
\draw[->,very thick,color=red] (s_0_14.center) -- (r_0_14.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_14_1) at (100mm,210mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_14_19) at (110mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_28) at (100mm,420mm) {};
\draw[->,very thick,color=red] (s_0_28.center) -- (r_0_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_3) at (110mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_17) at (120mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_14_1) at (140mm,15mm) {};
\draw[->,very thick,color=red] (s_14_1.center) -- (r_14_1.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_1_27) at (150mm,15mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_1_15) at (160mm,15mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_14_19) at (150mm,285mm) {};
\draw[->,very thick,color=red] (s_14_19.center) -- (r_14_19.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_19_13) at (160mm,285mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_19_9) at (170mm,285mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_3) at (150mm,45mm) {};
\draw[->,very thick,color=red] (s_28_3.center) -- (r_28_3.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_3_26) at (160mm,45mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_3_25) at (170mm,45mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_17) at (160mm,255mm) {};
\draw[->,very thick,color=red] (s_28_17.center) -- (r_28_17.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_17_29) at (170mm,255mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_17_12) at (180mm,255mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_1_27) at (190mm,405mm) {};
\draw[->,very thick,color=red] (s_1_27.center) -- (r_1_27.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_27_2) at (200mm,405mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_27_6) at (210mm,405mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_26) at (200mm,390mm) {};
\draw[->,very thick,color=red] (s_3_26.center) -- (r_3_26.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_26_5) at (210mm,390mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_19_13) at (200mm,195mm) {};
\draw[->,very thick,color=red] (s_19_13.center) -- (r_19_13.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_13_21) at (210mm,195mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_13_20) at (220mm,195mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_1_15) at (200mm,225mm) {};
\draw[->,very thick,color=red] (s_1_15.center) -- (r_1_15.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_15_18) at (210mm,225mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_15_16) at (220mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_25) at (210mm,375mm) {};
\draw[->,very thick,color=red] (s_3_25.center) -- (r_3_25.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_25_7) at (220mm,375mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_25_4) at (230mm,375mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_19_9) at (210mm,135mm) {};
\draw[->,very thick,color=red] (s_19_9.center) -- (r_19_9.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_9_23) at (220mm,135mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_9_22) at (230mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_17_29) at (210mm,435mm) {};
\draw[->,very thick,color=red] (s_17_29.center) -- (r_17_29.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_17_12) at (220mm,180mm) {};
\draw[->,very thick,color=red] (s_17_12.center) -- (r_17_12.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_27_2) at (240mm,30mm) {};
\draw[->,very thick,color=red] (s_27_2.center) -- (r_27_2.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_2_30) at (250mm,30mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_2_24) at (260mm,30mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_26_5) at (240mm,75mm) {};
\draw[->,very thick,color=red] (s_26_5.center) -- (r_26_5.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_27_6) at (240mm,90mm) {};
\draw[->,very thick,color=red] (s_27_6.center) -- (r_27_6.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_13_21) at (240mm,315mm) {};
\draw[->,very thick,color=red] (s_13_21.center) -- (r_13_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_13_20) at (250mm,300mm) {};
\draw[->,very thick,color=red] (s_13_20.center) -- (r_13_20.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_15_18) at (250mm,270mm) {};
\draw[->,very thick,color=red] (s_15_18.center) -- (r_15_18.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_18_10) at (260mm,270mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_18_8) at (270mm,270mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_25_7) at (250mm,105mm) {};
\draw[->,very thick,color=red] (s_25_7.center) -- (r_25_7.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_23) at (250mm,345mm) {};
\draw[->,very thick,color=red] (s_9_23.center) -- (r_9_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_22) at (260mm,330mm) {};
\draw[->,very thick,color=red] (s_9_22.center) -- (r_9_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_25_4) at (260mm,60mm) {};
\draw[->,very thick,color=red] (s_25_4.center) -- (r_25_4.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_15_16) at (260mm,240mm) {};
\draw[->,very thick,color=red] (s_15_16.center) -- (r_15_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_31) at (270mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_11) at (280mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_2_30) at (290mm,450mm) {};
\draw[->,very thick,color=red] (s_2_30.center) -- (r_2_30.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_2_24) at (300mm,360mm) {};
\draw[->,very thick,color=red] (s_2_24.center) -- (r_2_24.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_18_10) at (300mm,150mm) {};
\draw[->,very thick,color=red] (s_18_10.center) -- (r_18_10.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_18_8) at (310mm,120mm) {};
\draw[->,very thick,color=red] (s_18_8.center) -- (r_18_8.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_31) at (310mm,465mm) {};
\draw[->,very thick,color=red] (s_16_31.center) -- (r_16_31.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_11) at (320mm,165mm) {};
\draw[->,very thick,color=red] (s_16_11.center) -- (r_16_11.center);

>>>>

\node at (0mm,480mm) {Machine: gruyere, topology: binarytree};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (60mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (61mm,15mm) {};
\draw[->] (s_0_1.center) -- (r_0_1.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_1_3) at (71mm,15mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_1_4) at (81mm,15mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (71mm,30mm) {};
\draw[->] (s_0_2.center) -- (r_0_2.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_2_6) at (81mm,30mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_2_5) at (91mm,30mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_1_3) at (82mm,45mm) {};
\draw[->] (s_1_3.center) -- (r_1_3.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (92mm,45mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (102mm,45mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (101mm,60mm) {};
\draw[->,very thick,color=red] (s_1_4.center) -- (r_1_4.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (111mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (121mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_2_6) at (101mm,90mm) {};
\draw[->,very thick,color=red] (s_2_6.center) -- (r_2_6.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_6_14) at (111mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (121mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (111mm,75mm) {};
\draw[->,very thick,color=red] (s_2_5.center) -- (r_2_5.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_5_12) at (121mm,75mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (131mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (122mm,105mm) {};
\draw[->,very thick,color=red] (s_3_7.center) -- (r_3_7.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (132mm,105mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (142mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (122mm,120mm) {};
\draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (132mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (142mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (131mm,135mm) {};
\draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (141mm,135mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (151mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (141mm,210mm) {};
\draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_14_30) at (151mm,210mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_14_29) at (161mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (141mm,150mm) {};
\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (151mm,150mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (161mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (151mm,195mm) {};
\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_13_28) at (161mm,195mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_13_27) at (171mm,195mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (151mm,165mm) {};
\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (161mm,165mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_11_24) at (171mm,165mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (151mm,180mm) {};
\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_26) at (161mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_25) at (171mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (162mm,225mm) {};
\draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_15_31) at (172mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_14_30) at (171mm,450mm) {};
\draw[->,very thick,color=red] (s_14_30.center) -- (r_14_30.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_7_16) at (172mm,240mm) {};
\draw[->,very thick,color=red] (s_7_16.center) -- (r_7_16.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_18) at (172mm,270mm) {};
\draw[->,very thick,color=red] (s_8_18.center) -- (r_8_18.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (181mm,285mm) {};
\draw[->,very thick,color=red] (s_9_19.center) -- (r_9_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (181mm,300mm) {};
\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_13_28) at (181mm,420mm) {};
\draw[->,very thick,color=red] (s_13_28.center) -- (r_13_28.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (181mm,330mm) {};
\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_26) at (181mm,390mm) {};
\draw[->,very thick,color=red] (s_12_26.center) -- (r_12_26.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_14_29) at (181mm,435mm) {};
\draw[->,very thick,color=red] (s_14_29.center) -- (r_14_29.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (182mm,255mm) {};
\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_13_27) at (191mm,405mm) {};
\draw[->,very thick,color=red] (s_13_27.center) -- (r_13_27.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_25) at (191mm,375mm) {};
\draw[->,very thick,color=red] (s_12_25.center) -- (r_12_25.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_11_24) at (191mm,360mm) {};
\draw[->,very thick,color=red] (s_11_24.center) -- (r_11_24.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (191mm,345mm) {};
\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (191mm,315mm) {};
\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_15_31) at (192mm,465mm) {};
\draw[->,very thick,color=red] (s_15_31.center) -- (r_15_31.center);

### 2013-06-04 graphs/visu_gruyere_cluster.tex
Added forgotten file

\node at (0mm,480mm) {Machine: gruyere, topology: binarytree};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (60mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (61mm,15mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_1_3) at (71mm,15mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_1_4) at (81mm,15mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (71mm,30mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_2_6) at (81mm,30mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_2_5) at (91mm,30mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_1_3) at (82mm,45mm) {};
\draw[->] (s_1_3.center) -- (r_1_3.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (92mm,45mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (102mm,45mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (101mm,60mm) {};
\draw[->,very thick,color=red] (s_1_4.center) -- (r_1_4.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (111mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (121mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_2_6) at (101mm,90mm) {};
\draw[->,very thick,color=red] (s_2_6.center) -- (r_2_6.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_6_14) at (111mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (121mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (111mm,75mm) {};
\draw[->,very thick,color=red] (s_2_5.center) -- (r_2_5.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_5_12) at (121mm,75mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (131mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (122mm,105mm) {};
\draw[->,very thick,color=red] (s_3_7.center) -- (r_3_7.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (132mm,105mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (142mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (122mm,120mm) {};
\draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (132mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (142mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (131mm,135mm) {};
\draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (141mm,135mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (151mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (141mm,210mm) {};
\draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_14_30) at (151mm,210mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_14_29) at (161mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (141mm,150mm) {};
\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (151mm,150mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (161mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (151mm,195mm) {};
\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_13_28) at (161mm,195mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_13_27) at (171mm,195mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (151mm,165mm) {};
\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (161mm,165mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_11_24) at (171mm,165mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (151mm,180mm) {};
\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_26) at (161mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_25) at (171mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (162mm,225mm) {};
\draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_15_31) at (172mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_14_30) at (171mm,450mm) {};
\draw[->,very thick,color=red] (s_14_30.center) -- (r_14_30.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_7_16) at (172mm,240mm) {};
\draw[->,very thick,color=red] (s_7_16.center) -- (r_7_16.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_18) at (172mm,270mm) {};
\draw[->,very thick,color=red] (s_8_18.center) -- (r_8_18.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (181mm,285mm) {};
\draw[->,very thick,color=red] (s_9_19.center) -- (r_9_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (181mm,300mm) {};
\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_13_28) at (181mm,420mm) {};
\draw[->,very thick,color=red] (s_13_28.center) -- (r_13_28.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (181mm,330mm) {};
\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_26) at (181mm,390mm) {};
\draw[->,very thick,color=red] (s_12_26.center) -- (r_12_26.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_14_29) at (181mm,435mm) {};
\draw[->,very thick,color=red] (s_14_29.center) -- (r_14_29.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (182mm,255mm) {};
\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_13_27) at (191mm,405mm) {};
\draw[->,very thick,color=red] (s_13_27.center) -- (r_13_27.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_25) at (191mm,375mm) {};
\draw[->,very thick,color=red] (s_12_25.center) -- (r_12_25.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_11_24) at (191mm,360mm) {};
\draw[->,very thick,color=red] (s_11_24.center) -- (r_11_24.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (191mm,345mm) {};
\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (191mm,315mm) {};
\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_15_31) at (192mm,465mm) {};
\draw[->,very thick,color=red] (s_15_31.center) -- (r_15_31.center);

>>>>

\node at (0mm,480mm) {Machine: gruyere, topology: cluster};
\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (60mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (80mm,60mm) {};
\draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (90mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_16) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (110mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (120mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (130mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (80mm,120mm) {};
\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (90mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (100mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (110mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (120mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (130mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
\draw[->] (s_0_3.center) -- (r_0_3.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (120mm,360mm) {};
\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (130mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (140mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (150mm,360mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (120mm,180mm) {};
\draw[->,very thick,color=red] (s_4_12.center) -- (r_4_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (130mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (140mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (150mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (160mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (120mm,300mm) {};
\draw[->,very thick,color=red] (s_8_20.center) -- (r_8_20.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (130mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (140mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (150mm,300mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (121mm,165mm) {};
\draw[->] (s_8_11.center) -- (r_8_11.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (121mm,105mm) {};
\draw[->] (s_4_7.center) -- (r_4_7.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_16) at (130mm,240mm) {};
\draw[->,very thick,color=red] (s_4_16.center) -- (r_4_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (140mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (150mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (160mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (131mm,150mm) {};
\draw[->] (s_8_10.center) -- (r_8_10.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (131mm,90mm) {};
\draw[->] (s_4_6.center) -- (r_4_6.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (141mm,75mm) {};
\draw[->] (s_4_5.center) -- (r_4_5.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (141mm,405mm) {};
\draw[->] (s_24_27.center) -- (r_24_27.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (141mm,135mm) {};
\draw[->] (s_8_9.center) -- (r_8_9.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (141mm,345mm) {};
\draw[->] (s_20_23.center) -- (r_20_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (150mm,420mm) {};
\draw[->,very thick,color=red] (s_12_28.center) -- (r_12_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (160mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (170mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (180mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (151mm,330mm) {};
\draw[->] (s_20_22.center) -- (r_20_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (151mm,225mm) {};
\draw[->] (s_12_15.center) -- (r_12_15.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (151mm,285mm) {};
\draw[->] (s_16_19.center) -- (r_16_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (151mm,390mm) {};
\draw[->] (s_24_26.center) -- (r_24_26.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (161mm,315mm) {};
\draw[->] (s_20_21.center) -- (r_20_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (161mm,270mm) {};
\draw[->] (s_16_18.center) -- (r_16_18.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (161mm,375mm) {};
\draw[->] (s_24_25.center) -- (r_24_25.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (161mm,210mm) {};
\draw[->] (s_12_14.center) -- (r_12_14.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (171mm,255mm) {};
\draw[->] (s_16_17.center) -- (r_16_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (171mm,465mm) {};
\draw[->] (s_28_31.center) -- (r_28_31.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (171mm,195mm) {};
\draw[->] (s_12_13.center) -- (r_12_13.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (181mm,450mm) {};
\draw[->] (s_28_30.center) -- (r_28_30.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (191mm,435mm) {};
\draw[->] (s_28_29.center) -- (r_28_29.center);
